---
title: "Assignment 04"
author: "Jarvis Sanders"
date: "9/15/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Problem #1

By graphing the data this way I am able to see that the sepal width data rises to a certain point and then decreases steadily after that with local peaks, but ultimately decreasing. 

For sepal length, the data increases and decreases often. Multiple local peaks and lows. 

```{r}
library(ggplot2)
library(dplyr)

ggplot(data = iris) +
  geom_bar(mapping = aes (x = Sepal.Length))

ggplot(data = iris) +
  geom_bar(mapping = aes (x = Sepal.Width))
```


Problem #2

By adding the categorical variable species, I am able to take a closer look at each species of flower such as the sepal length and width in one graph. 

```{r}
ggplot(data = iris) +
  geom_histogram(aes(x = Sepal.Length, fill = Species), binwidth = 1) +
  labs(title = "Species", 
       x = "Sepal Length",
       y = "Sepal Width")
```

Problem #3

By graphing the data this way, I will be able to see the relationship between the width of the sepal of virginica, as well as the count of each occurence. 

```{r}
ggplot(data = iris) +
  geom_histogram(mapping = aes (x = Sepal.Width, fill = "virginica"), binwidth = 1)
```

